The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-19 manuscript.Rmd
[fix #27] add mention of how to prioritize specimens for digitization

For both the spelling of scientific names, and the geographic information, computing tools can be developed to detect issues and propose solutions. There are opportunities for services using publicly available data to be developed to make curators and collection managers aware of these issues so that they can fixed at the source. It however requires that resources are available to museum collections to address these issues.

@@

Another potential venue to improve the quality of the data in biodiversity information systems, is better incitives from journal editors and funding agencies for scientists to publish their occurrence records in databases alongside their papers as it is done for genetic data with GenBank [@Huang2011e].

>>>>

For both the spelling of scientific names, and the geographic information, computing tools can be developed to detect issues and propose solutions. There are opportunities for services using publicly available data to be developed to make curators and collection managers aware of these issues so that they can be fixed at the source. It however requires that resources are made available to museum collections to address these issues.

@@

Another venue to improve the quality of the data in biodiversity information systems, is better incitives from journal editors and funding agencies for scientists to publish their occurrence records in databases alongside their papers as it is done for genetic data with GenBank [@Huang2011e].

Specimens with accurate identifications and specimens that have been preserved in conditions such that it is possible to get DNA out of them should be prioritized, as they yield the most data that are relevant to biodiversity knowledge.
